Interval Probability for Fuzzy Quantum Theories

### 2016-07-29 prob.tex
prob.tex Filling the details to clarify the proof...

\begin{thm}[Shapley~\cite{Shapley1965,GilboaSchmeidler1994}]
Every convex interval-valued probability measure has a nonempty core,
where an interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
is convex if $\bar{\mu}\left(E\right)=\left[l\left(E\right),r\left(E\right)\right]$
and $l\left(E_{1}\cup E_{2}\right)+l\left(E_{1}\cap E_{2}\right)\ge l\left(E_{1}\right)+l\left(E_{2}\right)$
for all $E_{1},E_{2}\in\events$.\qed\end{thm}

@@

\begin{definition}[Quantum Interval-valued Probability Measure]\label{def:QuantumInterval-valuedProbability}
Given a Hilbert space $\Hilb$ with the set of quantum events~$\events$,
and a collection of intervals~$\mathscr{I}$, a \emph{quantum $\mathscr{I}$-interval-valued
probability measure} is a function~$\bar{\mu}:\events\rightarrow\mathscr{I}$
such that: 
\begin{itemize}
\item $\bar{\mu}(\mathbb{0})=\left[0,0\right]$, 
\item $\bar{\mu}(\mathbb{1})=\left[1,1\right]$, 
\item for any projection $P$,
$\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P\right)=1\tensor*[_{\mathscr{I}}]{-}{}\bar{\mu}\left(P\right)$, and
\item for a set of mutually orthogonal projections $P_{i}$, we have
$\bar{\mu}\left(\tensor*[_{\mathscr{O}}]{\sum}{_{i}}P_{i}\right)\subseteq\tensor*[_{\mathscr{I}}]{\sum}{_{i}}\bar{\mu}\left(P_{i}\right)$.
\end{itemize}
As before, we will only define a quantum interval-valued probability measure
with preposing $\mathscr{I}$ when we want to compare a quantum probability
measure and a quantum interval-valued probability measure.
\qed\end{definition}

@@

\begin{thm}\label{def:EmptyCoreQuantumInterval-valuedProbability}
There is a quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
such that $\mathrm{core}\left(\bar{\mu}\right)=\emptyset$.\qed\end{thm}

@@

\begin{example}[Three-dimensional quantum three-value interval-valued
probability measure]\label{ex:three-dimensional-three-value} Given
a three dimensional Hilbert space with an orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $.
Consider\emph{ $\mathscr{I}=\left\{ \necess,\imposs,\unknown\right\} $}
and $\ket{\ps}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{1})$. Let 
\begin{eqnarray*}
\bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps}) & = & \imposs\textrm{ ,}\\
\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})=\bar{\mu}(\mathbb{1}-\proj{\ps}) & = & \necess\textrm{ ,}\\
\bar{\mu}(P) & = & \unknown\textrm{, otherwise. }
\end{eqnarray*}
To verify $\bar{\mu}$ is a quantum interval-valued probability measure,
it is sufficient to check $\bar{\mu}\left(\proj{\psi_{1}}\tensor*[_{\mathscr{O}}]{+}{}\proj{\psi_{2}}\right)\subseteq\bar{\mu}\left(\proj{\psi_{1}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{\psi_{2}}\right)$
for orthogonal $\ket{\psi_{1}}$ and $\ket{\psi_{2}}$. This is easily
verified by enumerating all possible cases.

>>>>

\begin{thm}[Shapley~\cite{Shapley1965,GilboaSchmeidler1994}]
Every convex interval-valued probability measure has a nonempty core,
where an interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
is convex if $\bar{\mu}\left(E\right)=\left[l\left(E\right),r\left(E\right)\right]$
and $l\left(E_{1}\cup E_{2}\right)\ge l\left(E_{1}\right)\tensor*[_{\mathbb{R}}]{+}{}l\left(E_{2}\right)\tensor*[_{\mathbb{R}}]{-}{}l\left(E_{1}\cap E_{2}\right)$
for all $E_{1},E_{2}\in\events$.\qed\end{thm}

@@

\begin{definition}[Quantum Interval-valued Probability Measure]\label{def:QuantumInterval-valuedProbability}
Given a Hilbert space $\Hilb$ with the set of quantum events~$\events$,
and a collection of intervals~$\mathscr{I}$, a \emph{quantum $\mathscr{I}$-interval-valued
probability measure} is a function~$\bar{\mu}:\events\rightarrow\mathscr{I}$
such that: 
\begin{itemize}
\item $\bar{\mu}(\mathbb{0})=\left[0,0\right]$, 
\item $\bar{\mu}(\mathbb{1})=\left[1,1\right]$, 
\item for any projection $P$, 
\begin{equation}
\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P\right)=1\tensor*[_{\mathscr{I}}]{-}{}\bar{\mu}\left(P\right)\textrm{ ,}\label{eq:QuantumInterval-valuedProbability-Complement}
\end{equation}
\item for a set of mutually orthogonal projections $P_{i}$, we have 
\begin{equation}
\bar{\mu}\left(\tensor*[_{\mathscr{O}}]{\sum}{_{i}}P_{i}\right)\subseteq\tensor*[_{\mathscr{I}}]{\sum}{_{i}}\bar{\mu}\left(P_{i}\right)\textrm{ .}\label{eq:QuantumInterval-valuedProbability-Inclusion}
\end{equation}
\footnote{Let $\bar{\mu}\left(P\right)=\left[l\left(P\right),r\left(P\right)\right]$.
Then, $\bar{\mu}$ is called convex if $l\left(P_{1}P_{2}\right)\ge l\left(P_{1}\right)\tensor*[_{\mathbb{R}}]{+}{}l\left(P_{2}\right)\tensor*[_{\mathbb{R}}]{-}{}l\left(P_{1}\tensor*[_{\mathscr{O}}]{\vee}{}P_{2}\right)$
for all commuting $P_{1},P_{2}\in\events$. We may further define
a quantum Dempster-Shafer probability measure, and a quantum Dempster-Shafer
probability measure is always convex.}
\end{itemize}
As before, we will only define a quantum interval-valued probability
measure with preposing $\mathscr{I}$ when we want to compare a quantum
probability measure and a quantum interval-valued probability measure.
\qed\end{definition}

@@

\begin{thm}\label{def:EmptyCoreQuantumInterval-valuedProbability}
There is a (convex) quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
such that $\mathrm{core}\left(\bar{\mu}\right)=\emptyset$.\qed\end{thm}

@@

\begin{example}[Three-dimensional quantum three-value interval-valued
probability measure]\label{ex:three-dimensional-three-value} Given
a three dimensional Hilbert space with an orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $.
Consider\emph{ $\mathscr{I}=\left\{ \necess,\imposs,\unknown\right\} $}
and $\ket{\ps}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{1})$. Let 
\begin{eqnarray*}
\bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps}) & = & \imposs\textrm{ ,}\\
\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})=\bar{\mu}(\mathbb{1}-\proj{\ps}) & = & \necess\textrm{ ,}\\
\bar{\mu}(P) & = & \unknown\textrm{, otherwise. }
\end{eqnarray*}
To verify $\bar{\mu}$ is a quantum interval-valued probability measure,
first notice that $\bar{\mu}\left(\proj{P_{1}}\tensor*[_{\mathscr{O}}]{+}{}\proj{P_{2}}\right)\subseteq\bar{\mu}\left(\proj{P_{1}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{P_{2}}\right)$
implies equation (\ref{eq:QuantumInterval-valuedProbability-Inclusion})
by induction. Second, equation (\ref{eq:QuantumInterval-valuedProbability-Complement})
implies $\bar{\mu}\left(\mathbb{1}\right)\subseteq\bar{\mu}\left(\proj{P}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P\right)$.
Therefore, it is sufficient to check $\bar{\mu}\left(\proj{\psi_{1}}\tensor*[_{\mathscr{O}}]{+}{}\proj{\psi_{2}}\right)\subseteq\bar{\mu}\left(\proj{\psi_{1}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{\psi_{2}}\right)$
for orthogonal $\ket{\psi_{1}}$ and $\ket{\psi_{2}}$. This is easily
verified by enumerating all possible cases\footnote{This is the internal note for the detail of the proof, and can be
safely removed from the published version.}.
